### 2022-09-13 chapters/literature/draft_citations.tex
add : software optimization

JRAPL is another example of an energy measurement tool estimating tool that has been utilized in a variety of publications\cite{guimaraes2016some,liu2015data}.
This software enables for the energy usage of Java programs, functions, or even a block of code lines to be profiled and measured.
The measurements are heavily reliant on the data supplied by RAPL.
As a result, the global energy consumption collected by RAPL between two timestamps (the start and finish of the code to measure) is used to calculate the energy consumption of the Java code.
Tests using jRAPL should be done on a well-configured machine to minimize the impact of the operating system and user operations on the overall energy consumption of jRAPL.

@@

Beyond hardware components, the accuracy of power meters has also been questioned.
Inadomi~\emph{et~al.}~\cite{inadomi_analyzing_2015} used three different power measurement tools: RAPL, Power Insight\footnote{\url{https://www.itssolution.com/products/trellis-power-insight-application}} and BGQ EMON.
All of the three tools recorded the same $10\,\%$ of energy variation, that was supposedly related to the manufacturing process.

@@

We start with the work of \citeauthor{pereira2017energy} where they  did an energy consumption comparison analysis of the most popular programming languages.
Using the pareto optimum, the paper  provides recommendations on how to combine some of these languages to enhance code quality while taking into account execution time, memory utilization, and energy consumption using the pareto optimum. Some of the study's findings demonstrate that interpreted languages, such as Python, have lower energy efficiency than compiled languages, such as C or Rust. The research also offers language combinations that developers might use together to improve energy economy, execution speed, and memory utilization.
This paper's findings were based on the game benchmark, which is the most famous set of benchmarks that compares several programming languages.

@@

Other server works that have studied the impact of the website technology on the energy conusmptuon,\cite{philippot_characterization_2014},\cite{manotas2013investigating}. In their work~\cite{philippot_characterization_2014},\citeauthor{philippot_characterization_2014} measured the computer resources used during the loading of a website in a browser, such as memory utilization and energy consumption, for over 500 websites and proposed some best practices for developers.

% rosetta code \cite{nanz2015comparative} \cite{mirowski2020rosetta}

% network energy comparaison \cite{balasubramanian2009energy}

% Aequitas \cite{ribic2016aequitas}

% vm placement \cite{mishra2018energy}

% \citeauthor{mishra2018energy}

% static cost of Vms \cite{kurpicz2016much}

@@

java collection energy footprint  \cite{pinto2016comprehensive} \cite{fernandes2017assisting}

java classes energy footprint \cite{hasan2016energy}

>>>>

JRAPL is another example of an energy measurement tool estimating tool that has been utilized in a variety of publications~\cite{guimaraes2016some,liu2015data}.
This software enables for the energy usage of Java programs, functions, or even a block of code lines to be profiled and measured.
The measurements are heavily reliant on the data supplied by RAPL.
As a result, the global energy consumption collected by RAPL between two timestamps (the start and finish of the code to measure) is used to calculate the energy consumption of the Java code.
Tests using jRAPL should be done on a well-configured machine to minimize the impact of the operating system and user operations on the overall energy consumption of jRAPL.

@@

Beyond hardware components, the accuracy of power meters has also been questioned.
\citeauthor{inadomi_analyzing_2015}~\cite{inadomi_analyzing_2015} used three different power measurement tools: RAPL, Power Insight\footnote{\url{https://www.itssolution.com/products/trellis-power-insight-application}} and BGQ EMON.
All of the three tools recorded the same $10\,\%$ of energy variation, that was supposedly related to the manufacturing process.

@@

We start with the work of \citeauthor{pereira_energy_2017} where they  did an energy consumption comparison analysis of the most popular programming languages.
Using the pareto optimum, the paper  provides recommendations on how to combine some of these languages to enhance code quality while taking into account execution time, memory utilization, and energy consumption using the pareto optimum. Some of the study's findings demonstrate that interpreted languages, such as Python, have lower energy efficiency than compiled languages, such as C or Rust. The research also offers language combinations that developers might use together to improve energy economy, execution speed, and memory utilization.
This paper's findings were based on the game benchmark, which is the most famous set of benchmarks that compares several programming languages.

@@

Other works that have studied the impact of the website technology on the energy conusmptuon,\cite{philippot_characterization_2014,manotas_investigating_2013}. In their work~\cite{philippot_characterization_2014},\citeauthor{philippot_characterization_2014} measured the computer resources used during the loading of a website in a browser, such as memory utilization and energy consumption, for over 500 websites and proposed some best practices for developers.

Other works examined software energy consumption efficiency through source code changes and optimizations. For example, some papers [42, 122] studied the effect of Java collections on energy consumption, depending on the collection size and/or the most executed tasks on the collection (insertion, removal, search). They provided some insights into the energy efficiency of some collections for multiple scenarios. For example, Hasan et al. [52] compared the energy consumption of several Java data structures, analyzing the bytecode using the Wala framework8 and assessing the evolution of the energy consumption in different scenarios (insertion at the beginning, iteration, etc.). They also used some automated replacement of LinkedList and ArrayList to simulate best-and worst-case energy consumption scenarios in real production applications. Their study showed that using inappropriate collection can cause up to 300\% of energy consumption inefficiency.

As for the impact of the source code on the energy consumption, we can cite~\cite{pinto_comprehensive_2016,fernandes_assisting_2017} where the authors investigated the impact of Java collections on energy usage based on collection size and its usage (insertion, removal, search) and They provide some insights into the energy efficiency of specific collections under various scenarios.

\citeauthor{hasan_energy_2016} examinind the energy consumption of multiple Java data structures, analyzing the bytecode and evaluating the change in energy consumption in various circumstances(research,insertion, deletion, etc.). They also simulated best- and worst-case energy usage scenarios in real-world production systems by replacing the LinkedList and ArrayList, and discovered that incorrect collection can result in a 300\% increase in energy consumption\cite{hasan_energy_2016}.

Other studies\cite{longo_reducing_2019,kumar_energy_2017} looked into the energy use of Java primitive types, string operations, and the use of exceptions, loops, and arrays. \citeauthor{kumar_energy_2017}, for example, examined the energy usage of code snippets and micro-benchmarks and provided several conclusions, such as string concatenation would use less energy than StringBuilder and StringBuffer and static variables tends to consume 60\% more energy than instance variables.

\citeauthor{pereira_helping_2017} \cite{pereira_helping_2017} presented SPELL, a tool that helps developers spot energy leaks in their source code. Using a statistical spectrum-based analysis and JRAPL\cite{guimaraes2016some,liu_data-oriented_2015}, the tool locates energy-inefficient code fragments. According to the authors, it is language and context independent.

\subsection{Energy optimization in the execution phase}

The second part of this section will focus on energy optimization in the execution phase, where the goal is to optimize this energy consumption for already made software without making changes to the source code.

@@

java collection energy footprint

% java classes energy footprint \cite{hasan2016energy}
